Airy function: Kawai+Takei vs. Mari\~{n}o

### 2022-12-02 kawai+takei vs mariño.tex
minor changes

\begin{lemma}
Set $\lambda=0$. Let $\eta=2zx^{-2}$ then $\psi_-(x,\eta)=\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)$ is a solution of \eqref{eq:weber} if and only if $K_{1/4}(z)$ is a solution of the modified Bessel equation

\begin{equation}
\left[\frac{d^2}{dz^2}-1+\frac{1}{z}\frac{d}{dz}-\frac{1}{16 z^2}\right]\tilde{K}_{1/4}(z)=0
\end{equation}

@@

\begin{lemma}
Set $\lambda=0$. Let $\eta=2zx^{-2}$ then \[\psi_{-,B}(x,y)=x^{-3/2}\hat{\kappa}_{1/4}(\zeta)\] where $\hat{\kappa}_{1/4}(\zeta)=\mathcal{B}(\tilde{K}_{1/4})(\zeta)$. 
\end{lemma}

@@

\begin{align*}
\tilde{K}_{1/4}(z)&=\sqrt{\pi}e^{-z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(\frac{z}{2}\right)^{-n-1/2}
\end{align*}

@@

>>>>

\begin{lemma}
Set $\lambda=0$. Let $\eta=2zx^{-2}$ then $\psi_-(x,\eta)=\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)$ is a solution of \eqref{eq:weber} if and only if $\tilde{K}_{1/4}(z)$ is a formal solution of the modified Bessel equation

\begin{equation}\label{eq:Bessel 1/4}
\left[\frac{d^2}{dz^2}-1+\frac{1}{z}\frac{d}{dz}-\frac{1}{16 z^2}\right]\tilde{K}_{1/4}(z)=0
\end{equation}

@@

\begin{lemma}
Set $\lambda=0$. Let $\eta=2zx^{-2}$ then \[\psi_{-,B}(x,y)=x^{-3/2}\hat{\kappa}_{1/4}(\zeta)\] where $y=\frac{\zeta}{2}x^2$ and $\hat{\kappa}_{1/4}(\zeta)=\mathcal{B}(\tilde{K}_{1/4})(\zeta)$. 
\end{lemma}

@@

\begin{align*}
\tilde{K}_{1/4}(z)&=\sqrt{\pi}e^{-z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(2z\right)^{-n-1/2}
\end{align*}

@@

Furthermore, the modified Bessel equation \eqref{eq:Bessel 1/4} has another holomorphic solution $I_{1/4}(z)$ (which together with ${K}_{1/4}$ forms a basis) whose asymptotic behaviour is

\begin{equation}
\tilde{I}_{1/4}(z)=\frac{1}{\sqrt{\pi}}e^{z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(2z\right)^{-n-1/2}
\end{equation}
